---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# vici - Vaccine Induced Cellular Immunogenicity with Bivariate Modeling <a><img src='man/figures/logo.svg' align="right" height="139" /></a>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/vici)](https://CRAN.R-project.org/package=vici)
[![R-CMD-check](https://github.com/sistm/vici/workflows/R-CMD-check/badge.svg?branch=cran)](https://github.com/sistm/vici/actions/workflows/R-CMD-check.yaml?query=branch%3Acran)
[![Downloads](https://cranlogs.r-pkg.org/badges/vicis?color=blue)](https://www.r-pkg.org/pkg/vici)
<!-- badges: end -->

`vici` encapsulate a shiny app for accurate estimation of vaccine induced immunogenicity 
with bivariate linear modeling.

> Lhomme E, Hejblum BP, Lacabaratz C, Wiedemann A, Lelièvre JD, Lévy Y, Thiébaut R, Richert L (2020). Analyzing cellular immunogenicity in vaccine clinical trials: a new statistical method including non-specific responses for accurate estimation of vaccine effect. Journal of Immunological Methods, 477:112711. [doi:10.1016/j.jim.2019.112711](https://doi.org/10.1016/j.jim.2019.112711).

## Installation

You can install the released version of vici from the [CRAN](https://cran.r-project.org/) with:
``` r
install.packages("vici")
```
or get the development version from [GitHub](https://github.com/sistm/vici):
```{r GitHub-install, eval=FALSE}
#install.packages("remotes")
remotes::install_github("sistm/vici", ref = "cran")
```


Then you can launch the app with:
``` r
vici::run_app()
```

## Deployed VICI

 * Latest **development** version is deployed at https://shiny-vici.apps.math.cnrs.fr/  

 * Latest **stable** version is deployed at http://vici.bph.u-bordeaux.fr/

-- Boris Hejblum

